Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-07 paper.tex
Switch to bibtex

\begin{thebibliography}{9}
	\bibitem{1804.01082}
	Urmila Mahadev.
	\newblock Classical Verification of Quantum Computations, 2018;
	\newblock arXiv:1804.01082.

	\bibitem{quant-ph/0406180}
	Julia Kempe, Alexei Kitaev and Oded Regev.
	\newblock The Complexity of the Local Hamiltonian Problem, 2004,
	\newblock SIAM Journal of Computing, Vol. 35(5), p. 1070-1097 (2006),
		conference version in Proc. 24th FSTTCS, p. 372-383 (2004);
	\newblock arXiv:quant-ph/0406180.

	\bibitem{1109.0795}
	Matthew McKague.
	\newblock On the power quantum computation over real Hilbert spaces, 2011,
	\newblock Int. J. Quantum Inform., 11, 1350001 (2013);
	\newblock arXiv:1109.0795.
	\newblock DOI: 10.1142/S0219749913500019.

	\bibitem{0704.1287}
	Jacob D. Biamonte and Peter J. Love.
	\newblock Realizable Hamiltonians for Universal Adiabatic Quantum Computers, 2007,
	\newblock Phys. Rev. A 78, 012352 (2008).;
	\newblock arXiv:0704.1287.
	\newblock DOI: 10.1103/PhysRevA.78.012352.

	\bibitem{1904.06320}
	Alexandru Gheorghiu and Thomas Vidick.
	\newblock Computationally-secure and composable remote state preparation, 2019;
	\newblock arXiv:1904.06320.

	\bibitem{1708.02130}
	Urmila Mahadev.
	\newblock Classical Homomorphic Encryption for Quantum Circuits, 2017;
	\newblock arXiv:1708.02130.

	\bibitem{quant-ph/0301040}
	Dorit Aharonov.
	\newblock A Simple Proof that Toffoli and Hadamard are Quantum Universal, 2003;
	\newblock arXiv:quant-ph/0301040.

\end{thebibliography}

>>>>

\bibliographystyle{plain}
\bibliography{refs}
